The \kplr\ Catalog: Systematic probabilistic parameter estimation for every \kepler\ planet candidate

### 2013-12-29 document/ms.tex
initial description of target selection and data selection/preconditioning

Kepler data here.

Cut out bits around the transits, masking, etc.

Pre-conditioning by doing the local linear fits.

What gets passed forward:  Flattened light curve bits plus ivars?

@@

\paragraph{Generative model}
For this project, we assume a quadratic limb darkened light curve model
following Mandel \& Agol (CITE) and integrate over exposure time (Kipping
CITE, Appendix XXXX).
Since we don't want to be dependent on specific stellar parameters and since
we would like to make it easy to apply any new stellar catalogs, we don't use
physical orbits.
Instead, we parameterize the orbit using only ``observable'' parameters.
In particular, we use, for the star, the mean stellar flux \fstar, and the
parameters \qone\ and \qtwo\ of a quadratic limb darkening profile
(parameterized following Kipping CITE).
For each companion, we parameterize the orbit using period \period, epoch
\epoch, transit duration \duration, radius ratio \ror, and impact parameter
\impact.

@@

@@

For the probability of the data, we do [XXX chi-squared].

We choose to sample in parameters that are directly informed by the light
curve instead of the full set of physical parameters in the generative model.
The motivation for this choice is to attempt to find parameters that are close
to sufficient statistics for the light curves while being independent of the
stellar parameters.
To this end, we chose to parameterize each planet candidate with period
\period, epoch \epoch, radius \ror\ (measured in stellar radii), impact
parameter \impact, and transit duration \duration.
Our specific definition of transit duration deserves some discussion.
We define the transit duration as the time that it would take for the
center of the exoplanet to transit the center of the star (at $b=0$) instead
of choosing one of the standard definitions---for example $T_\mathrm{tot}$
from \citet{winn}.
We make the further simplifying assumption that the planet transits in a
straight line across the face of the star (WORDING).
In this limit, the conversion between \duration\ and the standard
$T_\mathrm{tot}$ used in the KOI catalog is
\begin{eqnarray}
T_\mathrm{tot} \approx \duration \, \sqrt{(1+\ror)^2 - \impact^2}
\end{eqnarray}

>>>>

The goal of this project is to propagate any information about exoplanets from
the \kepler\ light curves into a form that is more user friendly.
We target the list of all \kepler\ Objects of Interest (KOIs) listed on the
Exoplanet Archive\footnote{FIXME: URL} as planet candidates and confirmed
planets from quarters xxx--yyy.
Some of these candidates are certainly so-called false positives but we treat
them all equally so that the user can freely make their own target selection.
As our raw dataset, we start with the MAP-PDC light curves (CITE) provided by
MAST\footnote{FIXME: URL} and perform further preconditioning or
``de-trending'' to remove any remaining astrophysical or instrumental noise.

\paragraph{Target selection}
We downloaded the full list KOIs from the exoplanet archive using the \kplr\
Python module\footnote{\url{http://dan.iel.fm/kplr}} on SOME DATE and filtered
the list to only include planet candidates and confirmed planets as listed in
the database.
This list corresponds to the catalog from (SOME CITATION) generated by
searching the light curves from quarters xxx--yyy using the Transiting Planet
Search (TPS) module and then hand vetted (CITE).

\paragraph{Data selection}
Next, we downloaded all available PDC light curves (both short and long
cadence) for a given target and selected all data points within 4 transit
durations---as determined by the KOI catalog---of a transit.

\paragraph{Preconditioning}
Then, we mask the data within 1.5 transit durations and fit the maximum
likelihood line to the remaining data points.
Finally, we divide the full window by this model to generate a ``de-trended''
light curve.
This procedure has been applied successfully in the literature (Carter ETC
CITE) and it should be less destructive to transit signals than alternative
techniques like median filtering and ``robust'' regression.

@@

\paragraph{Generative model}
For this project, we assume a quadratic limb darkened light curve model
following Mandel \& Agol (CITE) and integrate over exposure time (Kipping
CITE, Appendix XXXX).
Since we don't want to be dependent on specific stellar parameters and since
we would like to make it easy to apply any new stellar catalogs, we don't use
physical orbits.
Instead, we parameterize the orbit using only ``observable'' parameters.
In particular, we use, for the star, the mean stellar flux \fstar, and the
parameters \qone\ and \qtwo\ of a quadratic limb darkening profile
(parameterized following Kipping CITE).
For each companion, we parameterize the orbit using period \period, epoch
\epoch, transit duration \duration, radius ratio \ror, and impact parameter
\impact.
\Tab{parameters} specifies the parameters used in this \paper\ and the
interim priors used.

@@

\Tab{parameters} lists the exact interim priors applied to each parameter.

@@
